---
title: "Alcohol vs Seat choice"
author: "Shauna Breazeal"
date: "09 Feb 2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r include=FALSE}
require(tidyverse)
require(tigerstats)
davisdata <- read.csv(file="UCDavis.csv")
```
 Our Goal is to answer this question Is there a difference between the alcohol consumed between the row
 you choose to sit in??

## Now with ggplot - first select the basic data

```{r}
basicCN <- ggplot(davisdata,aes(y=alcohol,x=Seat))
```
## Now add in boxplot

```{r}
basicCN + geom_boxplot()
```
  
  
### get fancy  

```{r}
basicCN + geom_boxplot(notch=TRUE,outlier.color = "red") + stat_boxplot(geom ='errorbar') + labs(title="Fancy notch boxplot \n with 2 lines")
```

This boxplot shows that the heavy drinkers are mostly seated in the back.


## Numerical Summarys 

```{r}
favstats(alcohol~Seat,data=davisdata)
```

People who sit in the back appear to drink atleast 3 times as much alcohol as the people in the front or the middle rows. 

## Inferential Tests

## Conclusions


